Journal and article coverage

### 2025-03-10 analysis/manuscript.qmd
Trend anaylsis replication

This section examines the open access uptake in hybrid journals, focusing on the influence of transformative agreements across hoaddata, Scopus and Web of Science.
A key objective of this analysis is to determine whether consistent results can be derived across these three data sources, despite their differing coverage and methodologies. 
By identifying potential variations, this study evaluates the suitability of open data approaches, such as hoaddata, as alternatives to proprietary bibliometric databases like Scopus and Web of Science.

>>>>

```{r, rep_data}
uptake_df <- readr::read_csv(here::here("data", "uptake_df.csv"))
```

This section examines the open access uptake in hybrid journals, focusing on the influence of transformative agreements across hoaddata, Scopus and Web of Science.
A key objective of this analysis is to determine whether consistent results can be derived across these three data sources, despite their differing coverage and methodologies.

```{r, plot_uptake_overview, fig.asp=.5}
uptake_df <- readr::read_csv(here::here("data", "uptake_df.csv"))

# Data prep
uptake_by_year <- uptake_df |>
  mutate(earliest_year = gsub("^20", "'", as.character(earliest_year))) |>
  group_by(earliest_year, src) |>
  summarize(
    n_articles = sum(n),
    n_oa_articles = sum(oa_articles),
    ta_oa_first_author_articles = sum(ta_oa_first_author_articles),
    ta_oa_corresponding_author_articles = sum(ta_oa_corresponding_author_articles)
  )

uptake_by_year_df <- uptake_by_year |>
  pivot_longer(cols = c(ta_oa_first_author_articles, ta_oa_corresponding_author_articles))

plot_oa_all <- ggplot(uptake_by_year_df, aes(x = earliest_year)) +
  geom_line(aes(y = n_oa_articles / n_articles, group = src, color = src), linetype = "solid") +
  geom_point(aes(y = n_oa_articles / n_articles, fill = src), alpha = 0.5, shape = 21) +
  scale_fill_manual(NULL,
    values = c(`HOAD` = "#595959", `Scopus` = "#2066a8", `Web of Science` = "#ae282c"),
    guide = "none"
  ) +
  scale_color_manual(NULL,
    values = c(`HOAD` = "#595959", `Scopus` = "#2066a8", `Web of Science` = "#ae282c")
  ) +
  scale_y_continuous(
    labels = scales::percent_format(),
    limits = c(0, NA),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(y = "Hybrid OA Uptake", x = NULL)

plot_ta_oa <- ggplot(filter(uptake_by_year_df, value > 0), aes(x = earliest_year)) +
  geom_line(aes(
    y = value,
    group = interaction(src, name),
    color = src, # Color by src only
    linetype = name
  )) + # Use linetype for name
  geom_point(aes(y = value, fill = src), alpha = 0.8, shape = 21) +
  scale_color_manual(NULL, values = c(`HOAD` = "#595959", `Scopus` = "#2066a8", `Web of Science` = "#ae282c")) +
  scale_fill_manual(NULL,
                    values = c(`HOAD` = "#595959", `Scopus` = "#2066a8", `Web of Science` = "#ae282c"),
                    guide = "none") +
  scale_linetype_manual(NULL,
    values = c(
      `ta_oa_first_author_articles` = "longdash",
      `ta_oa_corresponding_author_articles` = "dotted"
    ),
    labels = c(
      `ta_oa_first_author_articles` = "First",
      `ta_oa_corresponding_author_articles` = "Corresponding"
    )
  ) +
  scale_y_continuous(
    labels = function(x) format(x, big.mark = ",", scientific = FALSE),
    limits = c(0, NA),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(y = "Hybrid OA via Agreement", x = "Publication Year")

plot_ta_perc <- ggplot(filter(uptake_by_year_df, value > 0), aes(x = earliest_year)) +
  geom_line(aes(
    y = value / n_oa_articles,
    group = interaction(src, name),
    color = src, # Color by src only
    linetype = name
  )) + # Use linetype for name
  geom_point(aes(y = value / n_oa_articles, fill = src), alpha = 0.8, shape = 21) +
  scale_color_manual(NULL, values = c(`HOAD` = "#595959", `Scopus` = "#2066a8", `Web of Science` = "#ae282c")) +
  scale_fill_manual(NULL,
                    values = c(`HOAD` = "#595959", `Scopus` = "#2066a8", `Web of Science` = "#ae282c"),
                    guide = "none") +  
  scale_linetype_manual(NULL,
    values = c(
      `ta_oa_first_author_articles` = "longdash",
      `ta_oa_corresponding_author_articles` = "dotted"
    ),
    labels = c(
      `ta_oa_first_author_articles` = "First",
      `ta_oa_corresponding_author_articles` = "Corresponding"
    )
  ) +
  scale_y_continuous(
    labels = scales::percent_format(),
    limits = c(0, NA),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(y = "% of Hybrid OA via Agreement", x = NULL)

layout <- "ABC
EEE"

combined_plot <- wrap_plots(
  E = guide_area(),
  A = plot_oa_all,
  B = plot_ta_oa,
  C = plot_ta_perc,
  heights = c(1, 0),
  design = layout
) &
  theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.border = element_rect(color = "grey50", fill = NA),
      text = element_text(size = 10)
    ) &
  plot_annotation(tag_levels = "A")

combined_plot + plot_layout(guides = "collect")
```

Following @Jahn_2025, Figure ...

<!-- By identifying potential variations, this study evaluates the suitability of open data approaches, such as hoaddata, as alternatives to proprietary bibliometric databases like Scopus and Web of Science.-->

### 2025-03-10 analysis/manuscript.tex
Trend anaylsis replication

This section examines the open access uptake in hybrid journals,
focusing on the influence of transformative agreements across hoaddata,
Scopus and Web of Science. A key objective of this analysis is to
determine whether consistent results can be derived across these three
data sources, despite their differing coverage and methodologies. By
identifying potential variations, this study evaluates the suitability
of open data approaches, such as hoaddata, as alternatives to
proprietary bibliometric databases like Scopus and Web of Science.

>>>>

This section examines the open access uptake in hybrid journals,
focusing on the influence of transformative agreements across hoaddata,
Scopus and Web of Science. A key objective of this analysis is to
determine whether consistent results can be derived across these three
data sources, despite their differing coverage and methodologies.

\begin{center}
\includegraphics[width=0.99\linewidth,height=\textheight,keepaspectratio]{fig/plot_uptake_overview-1.pdf}
\end{center}

Following Jahn (2025), Figure \ldots{}
